---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# horf

<!-- badges: start -->
[![R-CMD-check](https://github.com/robingenuer/horf/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/robingenuer/horf/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The `horf` package contains necessary functions to reproduce the simulation experiments of the article Arlot and Genuer (XXXX). In this article the rate of convergence of Hold-Out Random Forests bias is studied. Thus, the package gives an implementation of this Random Forests variant and a plot function to visualize the bias convergence rate of trees v.s. forests.

## Installation

You can install the development version of horf from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("robingenuer/horf")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(horf)
## basic example code
```

